Mental Health Screening in CF

### 2023-01-13 Emily Muther/mental_health_screening.qmd
Update mental_health_screening.qmd

```{python}
import pandas as pd
# Data import
gad7 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv")
gad7 = gad7[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','GAD-7 Total Score','GAD-7 Totals']]
gad7.dropna(axis=0,inplace=True)
gad7.drop_duplicates(inplace=True)
phq9 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv")
phq9 = phq9[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','PHQ-9 Total Score (calculated)','PHQ-9 Totals']]
phq9.dropna(axis=0,inplace=True)
phq9.drop_duplicates(inplace=True)
psc = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv")
psc = psc[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','Score','PSC Totals']]
psc.dropna(axis=0,inplace=True)
psc.drop_duplicates(inplace=True)
# Merge
df = gad7.merge(phq9,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
df = df.merge(psc,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
# Rename
df.rename({'PAT_MRN_ID':'ID','CONTACT_DATE':'Date','AGE AT CONTACT ':'Age','GAD-7 Total Score':'GAD-7 Total','GAD-7 Totals':'GAD-7 Group','PHQ-9 Total Score (calculated)':'PHQ-9 Total','PHQ-9 Totals':'PHQ-9 Group','Score':'PSC-17 Total','PSC Totals':'PSC-17 Group'},inplace=True,axis=1)
```

@@

# Profiling

```{python}
from pandas_profiling import ProfileReport
profile = ProfileReport(df, title="Data Profiling Report")
profile.to_notebook_iframe()
```

>>>>

```{python}
import pandas as pd
# Data import
gad7 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv")
gad7 = gad7[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','GAD-7 Total Score','GAD-7 Totals']]
gad7.dropna(axis=0,inplace=True)
gad7.drop_duplicates(inplace=True)
phq9 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv")
phq9 = phq9[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','PHQ-9 Total Score (calculated)','PHQ-9 Totals']]
phq9.dropna(axis=0,inplace=True)
phq9.drop_duplicates(inplace=True)
psc = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv")
psc = psc[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','Score','PSC Totals']]
psc.dropna(axis=0,inplace=True)
psc.drop_duplicates(inplace=True)
# Merge
df = gad7.merge(phq9,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
df = df.merge(psc,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
# Rename
df.rename({'PAT_MRN_ID':'ID','CONTACT_DATE':'Date','AGE AT CONTACT ':'Age','GAD-7 Total Score':'GAD-7 Total','GAD-7 Totals':'GAD-7 Group','PHQ-9 Total Score (calculated)':'PHQ-9 Total','PHQ-9 Totals':'PHQ-9 Group','Score':'PSC-17 Total','PSC Totals':'PSC-17 Group'},inplace=True,axis=1)
# Pull in Trikafta data
eti = pd.read_excel("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/Copy of Trikafta Earliest and Most Recent Dates for Patients Over 12.xlsx",usecols=["MRN","Earliest Trikafta in PortCF"])
df = pd.merge(df,eti,left_on="ID",right_on="MRN")
# Pre/post
df["Post-Trikafta"] = df['Date'] > df['Earliest Trikafta in PortCF']
df["Post-Trikafta"].replace({False:"Pre",True:"Post"},inplace=True)
# Sort
df["Date"] = pd.to_datetime(df["Date"])
df.sort_values(by=["ID","Date"],inplace=True)
# Write to CSV
df.drop(["MRN"],axis=1,inplace=True)
df.to_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Cleaned/cf_mental_health_screening.csv",index=False)
```

@@

# Pre- vs. Post-ETI

```{r}
#| include: false
library(tidyverse)
library(arsenal)
```

```{r results="asis"}
df = read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Cleaned/cf_mental_health_screening.csv",na.strings ="")

means = df %>% group_by(ID,Post.Trikafta) %>% 
  summarise(`GAD 7 Total` = mean(GAD.7.Total,na.rm = T),
            `PHQ 9 Total` = mean(PHQ.9.Total,na.rm = T),
            `PSC 17 Total` = mean(PSC.17.Total,na.rm = T),.groups = "drop")

means$`GAD 7 Group` = cut(means$`GAD 7 Total`,c(-Inf,5,10,15,Inf),right = F,
                          labels = c("0-4(Minimal)","5-9(Mild)",
                          "10-14(Moderate)","15-21(Severe)"))

means$`PHQ 9 Group` = cut(means$`PHQ 9 Total`,c(-Inf,5,10,15,20,Inf),right=F,
                          labels = c("0-4(None)","5-9(Mild)","10-14(Moderate)",
                          "15-19(Moderately Severe)","20-27(Severe)"))

means$`PSC 17 Group` = cut(means$`PSC 17 Total`,c(-Inf,15,Inf),right = F,
                          labels = c("0-14(Low Risk)","15-34(High Risk)"))

# Remove missing and drop levels
keep = means %>% group_by(ID) %>% summarise(n=n()) %>% filter(n==2) %>% pull(ID)
means = means %>% filter(ID %in% keep)
means$`GAD 7 Group` = droplevels(means$`GAD 7 Group`)
means$`PHQ 9 Group` = droplevels(means$`PHQ 9 Group`)
means$`PSC 17 Group` = droplevels(means$`PSC 17 Group`)    
# Write 
write.csv(means,file="/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Cleaned/means.csv",row.names=F)

p <- paired(Post.Trikafta ~ `GAD 7 Total`+`GAD 7 Group`+
  `PHQ 9 Total`+`PHQ 9 Group`+
  `PSC 17 Total`+`PSC 17 Group`, 
            data = means, id = ID,numeric.test = "signed.rank",signed.rank.exact = F,
            numeric.stats = c("Nmiss","median","q1q3","range"))
summary(p,pfootnote=T)
```
